Factors Affecting Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations

### 2019-06-14 tex/highlights/highlights.tex
Added new highlights

>>>>

Preferential pathways may lead to the false conclusion that there are indoor sources present at a VI site.
Indoor concentrations vary roughly by a factor of three over a few days; up to an order of magnitude over a week.
Preferential pathways can dramatically increase the role of advective transport, provided there is a permeable subslab zone.
At sites with high advective transport potential, fluctuations in pressurization cause much of the observed variability.
Air exchange rate fluctuations significantly contribute with variability at sites with low advective transport potential.
